---
title: "Homework 5!"
author: "Jimmy Erkens"
date: "`r Sys.Date()`"
output: html_document
theme: journal
---

# Challenges!

## 1

Nicole reminded me to use `slice_sample()`, thanks Nicole!

## 2

I forgot to be using quantiles for bootstrapped confidence intervals, so I had to remember to do that.

## 3

I forgot basic syntax for matrices and had to refresh myself for a second. We're all good though!

# Load In the Data...

```{r, library, message = F}
library(tidyverse)
library(curl)
kandc <- read_csv(curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/KamilarAndCooperData.csv")); head(kandc)
```

## Baby's first linear model

```{r, lm}
hw5model <- lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data = kandc)
summary(hw5model)
hw5model$coefficients
```

The estimated log(HomeRange_km2) is -9.44123 when log(Body_mass_female_mean) = 0; this is $\beta_0$. As log(Body_mass_female_mean) increases by 1, the estimated log(HomeRange_km2) increases by 1.03; this is $\beta_1$.

# Bootstrapped

```{r, boot_the_strap}
set.seed(812) # set the seed

betas <- matrix(NA, nrow = 1000, ncol = 2) # initialize a NA matrix <3
for (i in 1:1000){
  new_sample = kandc %>% select(HomeRange_km2, Body_mass_female_mean) %>% # get the for loop going
    filter(is.na(HomeRange_km2) == F & is.na(Body_mass_female_mean) == F) %>% slice_sample(n = 100) 
  # don't want to deal w NA's in data
  # n = 100 bc that's actually a good sample size!
  betas[i, ] = lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data = new_sample)$coefficients
}
# subset our betas just for ease of whatever
beta0s <- betas[, 1]
beta1s <- betas[, 2]
```

Cool! We ran a bootstrapped estimate for our betas, what are our estimates?

```{r, estimates}
sebeta0 <- sd(beta0s); sebeta0 # these values are weak!
sebeta1 <- sd(beta1s); sebeta1
beta0CI <- quantile(beta0s, c(0.025, 0.975)); beta0CI
beta1CI <- quantile(beta1s, c(0.025, 0.975)); beta1CI
confint(hw5model)
```

Our bootstrapped method is ever so slightly more precise than the non-bootstrapped method! Who would've thought? 
